---
output:
  pdf_document:
    toc: false
    includes:
       in_header: codecheck-preamble.sty
    latex_engine: xelatex
---

```{r rsetup,eval=TRUE,include=FALSE}
require("codecheck")
require("knitr")
require("rprojroot")
require("yaml")
require("xtable")
require("tibble")
require("readr")
options(width = 60)
opts_chunk$set(cache=FALSE)

root = find_root("codecheck.yml")
```

```{r codecheck_logo, echo=FALSE,results='asis'}
latex_codecheck_logo()
```

```{r manifest, eval=TRUE, include=FALSE}
metadata = codecheck_metadata(root)
manifest = metadata$manifest

dest_dir = file.path(root, "codecheck", "outputs")
## Create the outputs directory if missing
if ( !dir.exists(dest_dir) ) {
  dir.create(dest_dir)
}

manifest_df = copy_manifest_files(root, metadata,
                                  dest_dir, keep_full_path = FALSE,
                                  overwrite = FALSE
                                  )
```

---
title: `r paste("CODECHECK certificate", metadata$certificate)`
subtitle: `r codecheck:::as_latex_url(metadata$report)`
---

```{r summary_metadata, echo=FALSE, results='asis'}
latex_summary_of_metadata(metadata)
```

```{r summary_manifest, echo=FALSE, results='asis'}
latex_summary_of_manifest(metadata, manifest_df, root)
```

# Summary

This project was easy to reproduce.  THe key requirements were clearly
stated, with the only additional requirement being the Control Systems
toolbox that was not mentioned in the repo.

The computation time was approximately 2 hours.

\clearpage

# CODECHECKER notes

Before running the code, I needed to install three toolboxes (two of
which were already noted in the author's readme): optimization,
global optimization, and control systems.  These were installed using
the 'Add ons' tool-bar item from from the top of the  Matlab GUI.

The repository already contained a folder called `Figures` which
contained matlab fig and png files.  I renamed this folder to
`Figures-safe` in case when I ran the code these figures would be
overwritten, and created a new `Figures` folder. (They were not
however overwritten).

The steps were to simply start matlab in the root folder and type
'main' at the prompt.  The code took 2 hours on a modern mac laptop to
complete.


Figures 1 through 7 then appeared on the screen and I saved them as
PNGs, and then quit Matlab.  The author's repository stated that only
case study 2 (2nd half of paper) was to be tested.

After finding the correspondence (during a workshop session) between
the Figures generated and the manuscript, I started to write the
codecheck.yml file and the report.

As the code was not on github, I simply deleted the .git folder and
created a new repository on github called `codecheckers/sddtp`.



## Recommendations

I suggest to the authors to consider the following suggestions for their next publication or workflow:

- You could save figures automatically to a folder, and give them
  semantically meaningful names.
- State how long the computation takes on a modern day laptop.
- State which figures in the manuscript correspond to outputs run by
  the code.

\clearpage

# Manifest files

```{r, echo=FALSE, results="asis", width=100}
for(i in c(1:nrow(manifest_df))) {
  path <- manifest_df[i,"dest"]
  if(stringr::str_ends(path, "(png|pdf|jpg|jpeg)")) {
    # include graphics with knitr has to happen at top level in chunks, see https://github.com/yihui/knitr/issues/1260
    # see also https://stackoverflow.com/questions/51268623/insert-images-using-knitrinclude-graphics-in-a-for-loop
    # knitr::include_graphics(manifest_df[1, "dest"], error = TRUE)
    # Therefore, generate Markdown code here:
    cat("## ", basename(path), "\n\n")
    cat("**Comment:** ", manifest_df[i,"comment"], "\n\n")
    cat(paste0("![", "Test ", "](", path, ")\n"))
  } else if (stringr::str_ends(path, "(Rout|txt)")) {
    cat("## ", basename(path), "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    cat(readLines(path), sep = "\n")
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else if (stringr::str_ends(path, "csv")) {
    cat("## ", basename(path), "\n\n", "Summary statistics of tabular data:", "\n\n")
    cat("\\scriptsize \n\n", "```txt\n")
    print(skimr::skim(read.csv(path)))
    cat("\n\n``` \n\n", "\\normalsize \n\n")
  } else {
    cat("## ", basename(path), "\n\n")
    cat("Cannot inlcude output file as figure.")
  }
  
  cat("\\clearpage \n\n")
}
```

\clearpage

## Acknowledgements

This codecheck was created collaboratively as part of the May 2024
workshop in Delft.  The author (Filip Sharma) was in the audience and
helped answer questions about his work.  The workshop participants
also collectively helped by determining how the figures generated by
the matlab corresponded to figures in the manuscript.  CODECHECK
acknowledges financial supported from the Mozilla foundation and the
Dutch Research Council, NWO.

# Citing this document

```{r, results='asis',echo=FALSE}
cite_certificate(metadata)
```

# About CODECHECK

This certificate confirms that the codechecker could independently
reproduce the results of a computational analysis given the data and
code from a third party.  A CODECHECK does not check whether the
original computation analysis is correct.  However, as all materials
required for the reproduction are freely available by following the
links in this document, the reader can then study for themselves the
code and data.


# About this document

This document was created using [R Markdown](https://rmarkdown.rstudio.com/) using the [`codecheck`](https://github.com/codecheckers/codecheck) R package.
`make codecheck.pdf` will regenerate the report file.

```{r}
sessionInfo()
```

```{r, include=FALSE, eval=FALSE}
# render this document in RStudio
rmarkdown::render("codecheck.Rmd", output_format = "pdf_document") 
```
